Learning Auditory Similarities Between Instrumental Playing Techniques

### 2019-10-01 paper/paper.tex
abstract v1

\begin{abstract}
Abstract here.
\end{abstract}

>>>>

\begin{abstract}

The notion of musical timbre have been extensively considered through the lens of the classic instrumentarium. For such a purpose, datasets of instruments played \textit{ordinario} are considered. On thoses datasets, computational model of timbre considering static spectral features such as Mel Frequency Cepstral coefficents displayed excellent performance.

The availability of richer musical datasets with many playing techniques, allows us to consider computational modeling of musical timbre with the outcomes of recent study  that stresses the importance of long term modulations in auditory perception.

We propose a timbre model that is based on a parametrized...

This model is evaluated in a retrieval task using a perceptually defined retrieval objective. Computational experiments demonstrates 1) the importance of handling long term modulations both in time and frequency, with a gain of $14\%$ in precision compared to Mfccs  2) the relevance of a learned layer that is able provide an average gain of $3\%$ in precision with a halving of the variance.

\end{abstract}
